Data_visualization

### 2018-10-16 Rmd/Data_visualization_common_names.Rmd
footnote for all the figures and now time to write a first abstract

@@

Each histogram shows the pollen ratio in percentage of the focal and non-focal species. The barplots are organized per family.

@@

```
\newpage
```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
pollen_ratios_solanaceae <- read.csv("Data/pollen_ratios_solanaceae.csv", header = T)
ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="Solanaceae", x="", y="Pollen mix ratio") +
  theme(axis.text.x=element_text(angle=60,hjust=1))+geom_hline(yintercept = 50)+
  scale_fill_manual(values=c("grey10", "grey60"))+ ylim(0,100)

```
\newpage
```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
pollen_ratios_convolvulaceae <- read.csv("Data/pollen_ratios_convolvulaceae.csv", header = T)
ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) + 
  geom_bar(stat='identity', position='dodge') +labs(title="Convolvulaceae", x="", y="Pollen mix ratio") + 
  theme(axis.text.x=element_text(angle=60,hjust=1))+geom_hline(yintercept = 50)+
  scale_fill_manual(values=c("grey10", "grey60"))+ ylim(0,100)

@@

@@

@@

```
\newpage

@@

@@

#Samte thing but without eggplant to improve visualization

@@

 ggplot(all, aes(x = reorder(species, pollen, FUN = median, na.rm = TRUE), y = pollen)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="All species(-Eggplant)",x="", y = "Pollen per anther")+aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.title = element_blank())

@@

 d <- d[d$species !="Eggplant",]

 ggplot(d, aes(x = reorder(species, ovules, FUN = median, na.rm = TRUE), y = ovules)) +
  geom_boxplot(outlier.shape = NA)+labs(title="All species(-Eggplant)",x="", y = "Nº of ovules")+
  aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+
  geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=family))+
  scale_color_manual(values = cbPalette) + 
  stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.title = element_blank())
```

@@

###POLLEN OVULE RATIO. TOTAL POLLEN PER FLOWER DIVIDED BY NUMBER OF OVULES

@@

@@

###STIGMA AREA. BRASSICACEAE+1 AND SOLANACEAE+1

@@

@@

###STIGMA AREA. ALL SPECIES, COLOUR PER SPECIES AND FAMILY

I like this type of density plot and I wanted to show the differences of stigma area of our 3 familys. The x axis shows the area in micrometers (um^2).

@@

###All Area per family

theme_set(theme_gray())
a <- ggplot(t_stigma_area, aes(x = um, fill = family)) +
  geom_density(alpha = 0.7) +
  theme(legend.position = c(0.8, 0.8))

@@

>>>>

*Abstract*

@@

@@

@@

**Figure 5**. Percentage of pollen deposited on the stigma of a subset of species of the Brassicaceae family with pollen mixes with the other two families (N=3). The black line represents the theoretical 50% pollen percentage of our mixes. The sample that was in ethanol was dried in a heater (few days) and then the solution was filled with sodium hydroxide to degradate the tissue. Once the tissue was soft, all the solution plus the tissue was placed on a grid and the whole quantity of the microtube was counted.

\newpage
```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
pollen_ratios_solanaceae <- read.csv("Data/pollen_ratios_solanaceae.csv", header = T)
ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="Solanaceae", x="", y="Pollen mix ratio") +
  theme(axis.text.x=element_text(angle=60,hjust=1))+geom_hline(yintercept = 50)+
  scale_fill_manual(values=c("grey10", "grey60"))+ ylim(0,100)

**Figure 6**. Percentage of pollen deposited on the stigma of a subset of species of the Solanaceae family with pollen mixes with the other two families (N=3). The black line represents the theoretical 50% pollen percentage of our mixes. The sample that was in ethanol was dried in a heater (few days) and then the solution was filled with sodium hydroxide to degradate the tissue. Once the tissue was soft, all the solution plus the tissue was placed on a grid and the whole quantity of the microtube was counted.

\newpage
```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
pollen_ratios_convolvulaceae <- read.csv("Data/pollen_ratios_convolvulaceae.csv", header = T)
ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) + 
  geom_bar(stat='identity', position='dodge') +labs(title="Convolvulaceae", x="", y="Pollen mix ratio") + 
  theme(axis.text.x=element_text(angle=60,hjust=1))+geom_hline(yintercept = 50)+
  scale_fill_manual(values=c("grey10", "grey60"))+ ylim(0,100)

**Figure 7**. Percentage of pollen deposited on the stigma of a subset of species of the Convolvulaceae family with pollen mixes with the other two families (N=3). The black line represents the theoretical 50% pollen percentage of our mixes. The sample that was in ethanol was dried in a heater (few days) and then the solution was filled with sodium hydroxide to degradate the tissue. Once the tissue was soft, all the solution plus the tissue was placed on a grid and the whole quantity of the microtube was counted.

@@

**Figure 8**. Total pollen deposited on the stigma of a subset of species of the Brassicaceae family with pollen mixes with the other two families (N=3). The sample that was in ethanol was dried in a heater (few days) and then the solution was filled with sodium hydroxide to degradate the tissue. Once the tissue was soft, all the solution plus the tissue was placed on a grid and the whole quantity of the microtube was counted.

@@

**Figure 9**. Total pollen deposited on the stigma of a subset of species of the Solanaceae family with pollen mixes with the other two families (N=3). The sample that was in ethanol was dried in a heater (few days) and then the solution was filled with sodium hydroxide to degradate the tissue. Once the tissue was soft, all the solution plus the tissue was placed on a grid and the whole quantity of the microtube was counted.

@@

**Figure 10**. Total pollen deposited on the stigma of a subset of species of the Convolvulaceae family with pollen mixes with the other two families (N=3). The sample that was in ethanol was dried in a heater (few days) and then the solution was filled with sodium hydroxide to degradate the tissue. Once the tissue was soft, all the solution plus the tissue was placed on a grid and the whole quantity of the microtube was counted.

@@

**Figure 11**. Pollen per anther of the ten species used in our artificial community belonging to three different families, Brassicaceae, Solanaceae and Convolvulaceae (N=20, I.aquatica N=10). Species are coloured by family. Pollen was counted with an hemocytometer.

\newpage
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
library(ggplot2)

@@

 ggplot(all, aes(x = reorder(species, pollen, FUN = median, na.rm = TRUE), y = pollen)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="All species(-Eggplant)",x="", y = "Pollen per anther")+aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.title = element_blank())
```

**Figure 12**. Pollen per anther of the species used in our artificial community belonging to three different families, Brassicaceae, Solanaceae and Convolvulaceae (N=20, I.aquatica N=10). Eggplant excluded in order to improve data visualization. Species are coloured by family. Pollen was counted with an hemocytometer.

@@

**Figure 13**. Number of ovules of the ten species (N=15). Species are coloured by family.

@@

@@

**Figure 14**. Pollen ovule ratio for all the species. Total pollen per flower was estimated by multiplying by the total number of anthers of the flower. Species are coloured by family.

@@

@@

**Figure 15**. Density plot of the stigmatic area. The measurements were conducted with a stereo microscope. Species are divided in two pannels of 5 species each (4 Brassicaceae + 1 Convolvulaceae and 4 Solanaceae + 1 Convolvulaceae). The x axis shows the area in square micrometers.

@@

@@

cowplot::plot_grid(a, labels = "AUTO")
```

**Figure 16**. Density plot of the stigmatic area for all the species. The measurements were conducted with a stereo microscope. The x axis shows the area in square micrometers.

t_stigma_area <- read.csv("Data/t_stigma_area.csv")
t_stigma_area_brassicaceae <- read.csv("Data/t_stigma_area_brassicaceae.csv")
t_stigma_area_solanaceae <- read.csv("Data/t_stigma_area_solanaceae.csv")
t_stigma_area_convolvulaceae <- read.csv("Data/t_stigma_area_convolvulaceae.csv")
###All Area per family
theme_set(theme_gray())
a <- ggplot(t_stigma_area, aes(x = um, fill = family)) +
  geom_density(alpha = 0.7) +
  theme(legend.position = c(0.8, 0.8))

@@

**Figure 17**. Density plot of the stigmatic area for the 10 species grouped by the three families: Brassicaceae, Solanaceae and Convolvulaceae. The measurements were conducted with a stereo microscope. The x axis shows the area in square micrometers.
